Joint Satellite Distributions in the Milky Way and Andromeda

### 2017-09-22 paper/paper.tex
plane center
new plot in paper
updated paper plots

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[LG satellite alignments]{Local Group Satellite Alignments}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{mstar.pdf}
\includegraphics[width=0.30\textwidth]{vmax.pdf}
\includegraphics[width=0.30\textwidth]{nsat.pdf}
\caption{Basic characteristics for the 11 pairs selected to be Local
  Group Analogues (circles). From left to right: stellar mass, maximum circular
  velocity and number of bright ($M_V<-9$) satellites.
  Galaxy A is the galaxy with the higher stellar mass.
  The squares represent the same characteristics for the observed
  Local Group. 
\label{fig:general}}
\end{figure*}

@@

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors homogeneously distributed over the
sphere.
Each vector represents the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of this unit vector with the position vector
for each satellite, this gives us the satellite distances to the
plane. 
The best plane is determined by the vector that gives the lowest
sample standard deviation in the satellite distances to the plane.
In the set of unit vectors to be considered we also include the vector
$\hat{I}_a$, which provides the exact solution in the case of $3$
satallites. 
We take the sample standard deviation as a measure of the plane's width
and denote by $\hat{p}$ the unit vector defining the direction
perpendicular to the best plane.

@@

\begin{figure*}
\centering
\includegraphics[width=0.48\textwidth]{planes.pdf}
\includegraphics[width=0.48\textwidth]{planes_normalized.pdf}
\caption{
Plane width as a function of the number of bright satellites.
Wider planes are expected as the satellite number increases.
\label{fig:planes}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.45\textwidth]{beta.pdf}
\includegraphics[width=0.45\textwidth]{beta_scatter.pdf}
\caption{
Cumulative distribution for the gelocity anisotropy $\beta$.
\label{fig:beta}}
\end{figure*}

\begin{figure}
\includegraphics[width=0.45\textwidth]{mu_ip_scatter.pdf}
\includegraphics[width=0.45\textwidth]{mu_ri_scatter.pdf}
\includegraphics[width=0.45\textwidth]{mu_rp_scatter.pdf}
\centering
\caption{A}
\end{figure}

>>>>

%=========================================================================
%		FRONT MATTER
%=========================================================================
\title[Satellites in the MW and M31]{Joint Satellite Distributions in the Milky Way and Andromeda}
\author[J.E. Forero-Romero \& V. Arias]
{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
Ver\'onica Arias$^1$\\
%%
$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
}

@@

\begin{figure*}
\centering
\includegraphics[width=0.7\textwidth]{planewidth_lg.pdf}
\includegraphics[width=0.7\textwidth]{ba_ratio_lg.pdf}
\includegraphics[width=0.7\textwidth]{ca_ratio_lg.pdf}
\includegraphics[width=0.7\textwidth]{mu_lg.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:general}}
\end{figure*}

@@

We fit satellite planes around each galaxy in the pair by randomly
generating 10000 unit vectors homogeneously distributed over the
sphere.
Each vector represents the direction perpendicular to a plane passing through
the main galaxy's center of mass. 
We compute the dot product of this unit vector with the position vector
for each satellite, this gives us the satellite distances to the
plane. 
The best plane is determined by the vector that gives the lowest
sample standard deviation in the satellite distances to the plane.
In the set of unit vectors to be considered we also include the vector
$\hat{I}_a$, which provides the exact solution in the case of $3$
satallites. 
We take the sample standard deviation as a measure of the plane's width
and denote by $\hat{p}$ the unit vector defining the direction
perpendicular to the best plane.
We also store the median of the satellite distances to the plane as a
measure of the plane's location with respect to the central galaxy.

@@
